Landscape composition and beneficial insects - time is important

### 2020-08-05 manuscript/manuscript_outline.Rmd
Added brief comment from PG

---
title: Landscape composition and beneficial insects
# subtitle: 
author:
  - name: Samuel Robinson
    email: samuel.robinson@ucalgary.ca
    affiliation: University of Calgary
    footnote: 1
  - name: Paul Galpern
    email: paul.galpern@ucalgary.ca
    affiliation: University of Calgary
address:
  - code: University of Calgary
    address: 2500 University Drive NW, Calgary, AB, Canada
footnote:
  - code: 1
    text: "Corresponding Author"
date: "Spring 2020"
abstract: Ground-dwelling arthropods are important generalist predators in prairie agro-ecosystems. However, we don't know what types of landscape features they live in. Some may act as sources of arthropods during some parts of the year, and sinks during others. We examined four widely-distributed species of arthropods, using functional regression to examine their habitat preferences. We found that trees/shrubs, and roadside grasses acted as sources of arthropods. Other features did not function as significant sources or sinks. Farmers should consider retaining these landscape features in order to preserve populations of helpful generalist predators in their crops.

>>>>

---
title: Landscape composition and beneficial insects - time is important
# PG: time is important in this paper - conservation efforts should consider temporal availability of resources
# Find the angle and write for this
# subtitle: 
author:
  - name: Samuel Robinson
    email: samuel.robinson@ucalgary.ca
    affiliation: University of Calgary
    footnote: 1
  - name: Paul Galpern
    email: paul.galpern@ucalgary.ca
    affiliation: University of Calgary
address:
  - code: University of Calgary
    address: 2500 University Drive NW, Calgary, AB, Canada
footnote:
  - code: 1
    text: "Corresponding Author"
date: "Spring 2020"
abstract: Ground-dwelling arthropods are important generalist predators in prairie agro-ecosystems. However, we don't know what types of landscape features they live in. Some may act as sources of arthropods during some parts of the year, and sinks during others. We examined four widely-distributed species of arthropods, using functional regression to examine their habitat preferences. We found that trees/shrubs, and roadside grasses acted as sources of arthropods. Other features did not function as significant sources or sinks. Farmers should consider retaining these landscape features in order to preserve populations of helpful generalist predators in their crops.
